### 2023-03-30 resilience-safe-down.tex
up

\begin{proof}
Downward compatibility of $\mathscr{S}=(S,\rightarrow, \leq)$ 
means that
for all $s_1, s_2, t_1 \in S$ with
$s_2 \leq s_1$ and $s_1 \to t_1$
there
exists
$t_2 \leq t_1$ such that $s_2 \to^* t_2$.

>>>>

\begin{proof}
Downward compatibility of $\mathscr{S}=(S,\rightarrow, \leq)$ 
means that
for all $s_1, s_2, t_1 \in S$ with
$s_2 \leq s_1$ and $s_1 \to t_1$
there
exists $t_2 \in S$ with
$t_2 \leq t_1$ and $s_2 \to^* t_2$.
